---
title       : Graph rotation
subtitle    : Rotating 2-dimensional Gaussian Samples
author      : Tingyao WU
job         : 
framework   : io2012        # {io2012, html5slides, shower, dzslides, ...}
highlighter : highlight.js  # {highlight.js, prettify, highlight}
hitheme     : tomorrow      # 
widgets     : [mathjax]            # {mathjax, quiz, bootstrap}
mode        : selfcontained # {standalone, draft}
knit        : slidify::knit2slides
---

## Introduction

- Goal

-- Generate a desinated number of two-dimensional samples with Gaussian distribution

-- Rotate the samples with a desinated angle

-- Be emcompassed by an ellipse

--- .class #id 

## Mathematical formula
- The multivariate Gaussian distribution

-- PDF: $p(\mathbf{x})=(2\pi)^{-\frac{k}{2}}|\Sigma|^{-\frac{1}{2}}e^{-\frac{1}{2}(\mathbf{x}-\mathbf{\mu})^{t} {\Sigma}^{-1}(\mathbf{x}-\mathbf{\mu})}$


- Formula of rotation with the angle $\theta$

Suppose the orignial sample is at $(x,y)$, after rotation with $\theta$ degree, the new sample $(x',y')$ is at 

$x'=x\times{\cos(\theta)}+y\times{\sin(\theta)}$, 

$y'=-x\times{\sin(\theta)}+y\times{\cos(\theta)}$


---

## Sample before rotation

- Original Samples


```{r, echo=FALSE}
library(plotrix)
#sample size
s <- 1000 
# the first dimension
mu.1 <- 0
sigma.1 <- 1
#the second dimension
mu.2 <- 4
sigma.2 <- 8

#angle
angle <- 0
#data generation
data.1 <- rnorm(s,mean=mu.1,sd=sigma.1)
data.2 <- rnorm(s,mean=mu.2,sd=sigma.2)
#plot with ellipse
plot(data.1,data.2,xlim=c(mu.2-3*sigma.2,mu.2+3*sigma.2),ylim=c(mu.2-3*sigma.2,mu.2+3*sigma.2),col="blue")
draw.ellipse(mean(data.1), mean(data.2), a = 3*sd(data.1), b = 3*sd(data.2), angle = 360-angle, deg = TRUE)
```


---

## Sample After rotation

- Sample after rotation 90 degree

```{r, echo=FALSE}
#angle
angle <- 90
#after rotation
newdata.1 <- data.1*cos(3.1415926*2*angle/360)+data.2*sin(3.1415926*2*angle/360)
newdata.2 <- -data.1*sin(3.1415926*2*angle/360)+data.2*cos(3.1415926*2*angle/360)
#plot
plot(newdata.1,newdata.2,xlim=c(mu.2-3*sigma.2,mu.2+3*sigma.2),ylim=c(mu.2-3*sigma.2,mu.2+3*sigma.2),col="blue")
                        
draw.ellipse(mean(newdata.1), mean(newdata.2), a = 3*sd(data.1), b = 3*sd(data.2), angle = 360-angle, deg = TRUE)

```

